---
title: "Wine Quality Feature Selection & Prediction Project"
author: "Autumn Heyman, Bethel Ikejiofor, Erin Weaver, Georgia Miller, Valerie Huston"
output: rmarkdown::github_document
---

Here we are taking a look at the quality of Vinho Verde wines within a region and select the more relevant physiochemical features that contribute to wine quality and in which ways. This will be achieved through the use of stepwise binary logistic regression.

# Importing Libraries
First we begin by *importing* our libraries.

```{r}
library(tidyverse)
library("caret")
library("lmtest")
library("magrittr")
library("dplyr")
library("tidyr")
library("popbio")
library("e1071")
```

# Importing our Dataset
Next we *import* our dataset.
```{r}
setwd('/Users/bethelikejiofor/Documents/GitHub/Fab-Five-Final-Project')
wine <- read.csv("./Data/WineQT.csv")

head(wine)
```

# Some Data Wrangling

We beging by reformatting column names so there are no spaces.
```{r}
names(wine) <- str_replace_all(names(wine), c(" "="."))
```

Next, we proceed to drop the ID column since it will not be used in our analysis. We will also take a look again at the head of the dataframe to make sure the wrangling changes took effect.
```{r}
wine = subset(wine, select = -c(Id))
head(wine)
```

# Assumptions Testing
For this project, rather than taking each of the individual quality levels and doing a logistic regression against them, we will recode the levels so wines either have either 'good' or 'poor' quality. Wines with a quality between 3 and 5 will fall into the 'poor' quality level and those between 6 and 8 will fall into the 'good' quality level.

## Recoding Wine Quality
```{r}
wine$qualityR <- NA
wine$qualityR[wine$quality==3] <- 0
wine$qualityR[wine$quality==4] <- 0
wine$qualityR[wine$quality==5] <- 0
wine$qualityR[wine$quality==6] <- 1
wine$qualityR[wine$quality==7] <- 1
wine$qualityR[wine$quality==8] <- 1
head(wine)
```

