---
title: "Wine Quality Feature Selection & Prediction Project"
author: "Autumn Heyman, Bethel Ikejiofor, Erin Weaver, Georgia Miller, Valerie Huston"
output:
  html_document:
    df_print: paged
---

Here we are taking a look at the quality of Vinho Verde wines within a region and select the more relevant physiochemical features that contribute to wine quality and in which ways. This will be achieved through the use of stepwise binary logistic regression.

# Importing Libraries
First we begin by *importing* our libraries.

```{r}
library(tidyverse)
library("caret")
library("lmtest")
library("magrittr")
library("dplyr")
library("tidyr")
library("popbio")
library("e1071")
```

# Importing our Dataset
Next we *import* our dataset.
```{r}
setwd('/Users/bethelikejiofor/Documents/GitHub/Fab-Five-Final-Project')
wine <- read.csv("./Data/WineQT.csv")

head(wine)
```

# Some Data Wrangling

We beging by reformatting column names so there are no spaces.
```{r}
names(wine) <- str_replace_all(names(wine), c(" "="."))
```

Next, we proceed to drop the ID column since it will not be used in our analysis. We will also take a look again at the head of the dataframe to make sure the wrangling changes took effect.
```{r}
wine = subset(wine, select = -c(Id))
head(wine)
```

# Assumptions Testing
For this project, rather than taking each of the individual quality levels and doing a logistic regression against them, we will recode the levels so wines either have either 'good' or 'poor' quality. Wines with a quality between 3 and 5 will fall into the 'poor' quality level and those between 6 and 8 will fall into the 'good' quality level.

## Recoding Wine Quality
```{r}
wine$qualityR <- NA
wine$qualityR[wine$quality==3] <- 0
wine$qualityR[wine$quality==4] <- 0
wine$qualityR[wine$quality==5] <- 0
wine$qualityR[wine$quality==6] <- 1
wine$qualityR[wine$quality==7] <- 1
wine$qualityR[wine$quality==8] <- 1
head(wine)
```
## Running the Base Logistic Model
```{r}
mylogit <- glm(qualityR ~ fixed.acidity + volatile.acidity + citric.acid + 
                  residual.sugar + chlorides + free.sulfur.dioxide + total.sulfur.dioxide+
                  density + pH + sulphates + alcohol, data = wine, family="binomial")
```

## Predicting Wine Quality
```{r}
probabilities <- predict(mylogit, type = "response")
```

Here, I will take the average of the probabilities from the prediction and anything that is above that probability will be classified as a good quality wine and anything below it will be classified as a poor quality wine.
```{r}
avg <- mean(probabilities)
wine$Predicted <- ifelse(probabilities > avg, "good", "poor")
head(wine)
```

## Recoding the Predicted Variable

```{r}
wine$PredictedR <- NA
```
```{r}
wine$PredictedR[wine$Predicted=="good"] <- 1
wine$PredictedR[wine$Predicted=="poor"] <- 0
head(wine)
```

## Converting Variables to Factors
```{r}
wine$PredictedR <- as.factor(wine$PredictedR)
wine$qualityR <- as.factor(wine$qualityR)
head(wine)
```

## Creating a Confusion Matrix
```{r}
conf_mat <- caret::confusionMatrix(wine$PredictedR, wine$qualityR)
conf_mat
```

Thankfully, all of the four cells are above 5 so the sample size minimum is met.

## Logit Linearity

```{r}
wine1 <- wine %>% dplyr::select_if(is.numeric)
predictors <- colnames(wine1)
wine1 <- wine1 %>% mutate(logit=log(probabilities/(1-probabilities))) %>%
gather(key= "predictors", value="predictor.value", -logit)
```
```{r}
ggplot(wine1, aes(logit, predictor.value))+
geom_point(size=.5, alpha=.5)+
geom_smooth(method= "loess")+
theme_bw()+
facet_wrap(~predictors, scales="free_y")
```
Most of the variables do not seem to have a linear logit relationship with wine quality so the assumption is not met. We will however proceed with our analyses.

## Multicollinearity

Insert Valerie's code.
```{r}

```

