---
title: "Wine Quality Feature Selection & Prediction Project"
author: "Autumn Heyman, Erin Weaver, Georgia Miller, Valerie Huston"
output:
  html_document:
    df_print: paged
---

# Importing Libraries
First we begin by *importing* our libraries.

```{r}
library(tidyverse)
library("caret")
library("lmtest")
library("magrittr")
library("dplyr")
library("tidyr")
library("popbio")
library("e1071")
library("PerformanceAnalytics")
library("corrplot")
library(corpcor)
library("MASS")
```

## Multicollinearity
# Importing our Dataset
Next we *import* our dataset.
```{r}
setwd('/Users/bethelikejiofor/Documents/GitHub/Fab-Five-Final-Project')
wine <- read.csv("./Data/WineQT.csv")

head(wine)
```
### Converting to Numeric
To ensure the data was continuous, I will covert the new quality column to s numeric column.
```{r}
wine$qualityR2 <- as.numeric(wine$qualityR)
head(wine)
```

### Subsetting Data
I will create a data frame with the numeric quality column and the independent variables.
```{r}
wine_subset <- wine[, c(1,2,3,4,5,6,7,8,9,10,11,16)]
```

### Testing for Correlation
```{r}
chart.Correlation(wine_subset, histogram=FALSE, method="pearson")
```

```{r}
corr_matrix <- cor(wine_subset)
corr_matrix
```

```{r}
corrplot(corr_matrix, type="upper", order="hclust", p.mat = corr_matrix, sig.level = 0.01, insig="blank")
```

## Testing for Multicollinearity
```{r}
cor2pcor(cov(wine_subset))
cor2pcor(cov(wine_subset))
```

```{r}
winecor <- ginv(cor(wine_subset))
colnames(winecor) <- colnames(wine_subset)
rownames(winecor) <- colnames(wine_subset)
winecor
```

```{r}
corrplot(corr = winecor, method = "number", is.corr = FALSE)
```

The VIFs for fixed acidity and density are greater than 5 and may be causing multicollinearity to be present in the data.


## Test for Independence of Errors

### graph
```{r}
plot(mylogit$residuals)
```


We are looking for pretty even distribution of points all the way across the x axis. We have that, so have met the assumption of independent errors.






### Durbin-Watson Test

Just for the sake of double checking for independence errors:
```{r}
dwtest(mylogit, alternative="two.sided")
```
Output:
Durbin-Watson test

data:  mylogit
DW = 1.8156, p-value = 0.001465
alternative hypothesis: true autocorrelation is not 0


Since DW value is within 1-3 range, we have met the assumption of independent errors. 



